This is an example of article title

### 2019-08-29 paper.tex
lstset
things

n = 100000
timestamps = sort(DateTime.(now() .- Millisecond.(rand(1:10^6, n))))
x = cumsum(randn(n)) .± rand(n)./10

@@

@@

>>>>

function random_observations(n)
    timestamps = sort(DateTime.(now() .- Millisecond.(rand(1:10^6, n))))
    x = cumsum(randn(n)) .± rand(n)./10
    table((time=timestamps, x=x))
end

observations = random_observations(100000)

@@

Finally, the Measurements.jl defines how plotting must be performed for an array of measurements, hence, for example a plotting tool that knows the tabular structure of JuliaDB, such as StatPlots.jl can be readily used to plot the table. The plotting automatically shows error bars representing uncertainty.

@@

\section{Benchmarks}
